---
title: "linear model from Web"
author: "Seth Guzman"
date: "Put semester and year"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```
## Introduction 
The goal of this statistical report is to find a 95% prediction interval for  SIMS when ARM has a value of 88 and GRIP has a value of 94. In order to achieve this we will compare model 1-3. we will be using the num-num helper file because both 


## Model 1 SIM~ARMS

## Results


## Graphical Results
```{r}
model.1 <- lm(SIMS~ARM,data)
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```



   ARM and SIMS both increase linearly with each other. 


##  Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```
The correlation is .68 proving that arm strength is related to sim score.




## Inferential results

```{r}
model.1 <- lm(SIMS~ARM,data)
summary.lm(model.1)
```

both $b_0$ (intercept) and $b_1$ (coefficeient) of ARM strength are significant  due to the small p value of both (<2e-16)




```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval="predict")
```



the prediction interval is from -1.726209 to 3.138977 for SIMS score.




## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
model.2 <- lm(SIMS~GRIP,data)
plot(SIMS~GRIP,data=data)
abline(model.2, col='red')
```


As GRIP increases in value SIMS increases alongside it linearly as shown by the points


### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
SIMS and GRIP have a correlation of .63 proving they are linked together
### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data)
summary.lm(model.2)
```

both $b_0$ (intercept) and $b_1$ (coefficeient) of GRIP strength are significant  due to the small p value of both (<2e-16)


#### predict model.2 at target point

```{r}
newdata = data.frame(SIMS=88, GRIP=94)
predict(model.2, newdata, interval="predict")
```



The prediction interval for arm strength ranges from as low as -3.107 to 2.035


#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

## Numerical results
```{r}
cor(SIMS~ARM+GRIP, data = data)
```

The correlation is .73 proving ARM+GRIP is related to SIMS score.
## Inferential Results

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data)
print(summary(model.3))
```
`


ARM and GRIP are both closely related because both of there coefficient p value is extremely small.

  
## Prediction Interval

```{r}
newdata = data.frame(ARM= 88 , GRIP=94)
predict(model.3, newdata, interval = "predict")
```

The prediction interval is from as low as -2.132373 to as high as 2.431668 for SIM score

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.3,model.1)
```

i reject the null hypothesis because of how low the p value is (.0000049). model 1 is better then model 2 because of model 1 rss score being lower then model 2

### Model.2 vs Model.3


```{r}
anova(model.3,model.2)
```

model three has a lower rss score then model two therefore making it a smaller model.

## Discussion and Conclusion 

Through comparing models to each other ive found model 3 to be the best because it has a smalller rss score then all the models



